---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# epidatr

<!-- badges: start -->
<!-- badges: end -->

The goal of epidatr is to provide a convenient way for R users to access data 
released by the [Delphi group's](https://delphi.cmu.edu/) 
[Epidemiological API](https://cmu-delphi.github.io/delphi-epidata/).
Currently, it provides accesss only to the COVID-19 API endpoints. This is not
an official R client for the API in any sense. Rather it is simply one 
contributed option.

## Installation

This package may be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("e3bo/epidatr")
```

 

## Example

View the covid data available:

```{r}
library(epidatr)
covidcast(source = "covidcast_meta")$epidata
```

Make a request with the default query:

```{r}
covidcast()
```

Choose a different set of dates and view the data frame:

```{r}

covidcast(time_values = "20200412-20200415,20200418")$epidata
```

Provide a query string:
```{r}
query <- "source=covidcast&data_source=fb-survey&signal=smoothed_cli&time_type=day&geo_type=county&time_values=20200406&geo_value=01000"
covidcast(query=query)$epidata
```
